### 2014-11-10 Conclusion.tex
Finished a pass through whole paper; now need to think about shrinking

In this paper we developed a modular proof structure for distributed
shared-memory hardware systems, corresponding naturally to the modularization seen in
hardware implementation. This makes it feasible for verification of the
system to be carried out throughout the implementation process without
disrupting the architect's design process.

>>>>

In this paper we developed a modular proof structure for distributed
shared-memory hardware systems, corresponding naturally to the modularization seen in
hardware implementations. Our approach allows verification of the
system to be carried out throughout the implementation process without
disrupting the architect's design process.
